---
title: "In Class Lab - DIY Functions"
author: "Dr. Shoemaker"
date: "DATA 2401"
output: html_document
---
**Note: Your exam will be in a similar format to this (RMarkdown File with Questions and Code chunks for your answers), so make sure you have the process for knitting to html working.** 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## In Class Activity 
The questions from your notes today are below, please copy your answers them here! Then complete the two new tasks, and attempt the "hard mode" if you have time. 

1. Write your own function that takes the temperature in Fahrenheit as an argument and returns the Celcius equivalent. 

```{R}
#Function to convert fahrenheit to celsius
fahrenheit_to_celsius <- function(fahrenheit) { 
  celsius <- (fahrenheit - 32) * 5 / 9 
  return(celsius)
}

#Using the function
fahrenheit_to_celsius(100)

```

2. Expand that function so that it takes a temperature in Fahrenheit and a distance in feet and returns **both** the temperature in Celcius and the distance in meters (you'll likely need to remember the `c()` function!)


```{r}

#Function to convert both celsius and meters
convert_values <- function(fahrenheit, feet) {
  celsius <- (fahrenheit - 32) * 5 / 9
  meters <- feet * 0.304
  return(c(celsius, meters)) #'c' combines
}

#Using the function
convert_values(212, 3)



```


3. Write a function that prints out a statement of whether the number passed as an argument is positive, negative or 0. 

```{R}

check_num <- function(num) {
  if(num > 0) {
    print("Number is positive.")
  } else if (num < 0) {
    print("Number is negative.")
  } else {
    print("Number is zero.")
  }
}

check_num(100)

```

4. Write a function that returns the absolute value of the number passed as an argument.
   + Don't use `abs()`. Use the flow from problem 1 and multiply by negative one as necessary. 
   
```{r}
absolute_value <- function(num) {
  if (num < 0) {
    return(num * -1)
  } else {
    return(num)
  }    
}

absolute_value(0)
```

5. Hard mode: add an error check to that function that prints out the string "Please pass a numerical value to this function" if the user passes the function a string. 
   + There are functions that check and return T/F: `is.numeric()` or `is.character()` would be relevant here
   
```{r}
absolute_value <- function(num) {
  if(is.character(num)) {
    print("Please pass a numerical value to this function")
    return(NULL)
  }
  
  if(num < 0) {
    return(num * -1)
  } else {
    return(num)
  }
}

absolute_value("thirty four")
absolute_value(34)
```
   
   






```

